Contracts for unions and intersections are hard for Nickel

### 2021-04-27 paper.tex
Better size for the todo boxes
Some notes
Note: Typescript's type are static

  \usepackage{xargs}
  \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
  % ^^ Need for pgfsyspdfmark apparently?
  \ifx\noeditingmarks\undefined
      \setlength{\marginparwidth}{1.2cm} % A size that matches the new PACMPL format
      \newcommand{\Red}[1]{{\color{red}{#1}}}
      \newcommand{\newaudit}[1]{{\color{blue}{#1}}}
      \newcommand{\note}[1]{{\color{blue}{\begin{itemize} \item {#1} \end{itemize}}}}
      \newenvironment{alt}{\color{red}}{}

@@

\section*{Introduction}
Intro\unsure{todo}

\section{Background on union types}

@@

This dilemma is naturally solved by gradual typing\cite{Siek06gradualtyping}
which mixes both static and dynamic typing. Unlike gradually-typed languages
like TypeScript, we do not seek to build a complex type system that tries hard
to accept most of the idioms naturally arising in dynamically typed code.
Rather, we choose to provide a reasonably expressive type system with good
inference properties, which makes typing functions operating on generic data easy,
but may require using untyped code for more exotic expressions.  In any case,
this is not a surrender, as Nickel provides a complementary mechanism for more
advanced data validation: contracts.

>>>>

  \usepackage{xargs}
  \usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
  % ^^ Need for pgfsyspdfmark apparently?
  \ifx\noeditingmarks\undefined
      % \setlength{\marginparwidth}{1.2cm} % A size that matches the new PACMPL format
      \newcommand{\Red}[1]{{\color{red}{#1}}}
      \newcommand{\newaudit}[1]{{\color{blue}{#1}}}
      \newcommand{\note}[1]{{\color{blue}{\begin{itemize} \item {#1} \end{itemize}}}}
      \newenvironment{alt}{\color{red}}{}

@@

\section*{Introduction}
Intro\unsure{todo}
\info{Goals of the paper: position paper: unions/intersections nice in
theory problematic in practice. In particular non-orthogonal with the
rest of the features of your language.}
\section{Background on union types}

@@

This dilemma is naturally solved by gradual typing\cite{Siek06gradualtyping}
which mixes both static and dynamic typing. Unlike gradually-typed languages
like TypeScript\unsure{Todo: explain that typescript uses unions as
  static typing whereas we are speaking of dynamic contracts}, we do not seek to build a complex type system that tries hard
to accept most of the idioms naturally arising in dynamically typed code.
Rather, we choose to provide a reasonably expressive type system with good
inference properties, which makes typing functions operating on generic data easy,
but may require using untyped code for more exotic expressions.  In any case,
this is not a surrender, as Nickel provides a complementary mechanism for more
advanced data validation: contracts.
